---
title: "Soni_M1_Project1"
author: "Manan Soni"
date: "1/17/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## a. A scatter plot of the Sales ~ Tempareture data

Scatter plot based on provided data of sales and temperature is shown(Fig.1) below.

```{r}
sales <- c(7,11,15,20,19,11,18,10,6,22) # creating Sales Vector
temperature = c(69,81,77,84,80,97,87,70,65,90) # creating Temperature Vector
library(ggplot2)
ggplot(data.frame(sales,temperature), aes(x = temperature , y=sales , color = ..y..)) +
  geom_point(size=4) +
  labs(
    title = "Fig.1 Sales ~ Temperature", # adds title
    x = "Temperature (°F)", # x-axis label
    y = "Sales\n", # y-axis label
    color = "Sales" # color legend
  ) + 
  scale_color_gradient(low="pink", high="red") +
  theme_light() +
  theme(
    plot.title = element_text(hjust = 0.5),
  ) # Plotting on Scatter Graph 
```

## b. The mean temperature

```{r}
# mean(*vector to calculate mean*)
cat('Mean of Tempareture Vector is ',mean(temperature))
```

## c. Displaying the data after manipulating **sales** vector

```{r}
sales <- c(sales[-3]) # removing 3rd element of sales
sales
sales <- append(sales,16,2) # inserting 16 as new 3rd element of sale
sales
```

## d. Display the names vector

```{r}
names <- c("Tom","Dick","Harry")
names
```

## e. Displaying the matrix of 5 row and 2 column of 10 integers

``` {r}
matrixx <- matrix(c(1:10),nrow=5,byrow=FALSE) # creating Matrix of 2 column and 5 row
matrixx
```

## f. Display the icSales data frame

```{r}
icSales <- data.frame('Sales'= sales,'Temperature' = temperature) #LHS defines column heads in data frames
icSales
```

## g. Display the summary of the icSales data frame

`summary` is a built-in function which provide summary of a data-frame.

```{r}
icSalesSummary = summary(icSales)
icSalesSummary
```

## h. Display the variables only from the Student.csv data set.

`names` is also a built-in function to get all the variables/column heads of given.

```{r}
student_data = read.csv("./Student.csv") # Opening Student.csv file
names(student_data) # Printing Variables of Student.csv
```

## i. A summary of the information you learned about the data sets based on the instructions you followed.

```{}
# check if package exist
if(!require('vcd',character.only = TRUE)) install.packages('vcd')
# importing vcd
library(vcd)

# creating Vectors
sales <- c(7,11,15,20,19,11,18,10,6,22)
temperature = c(69,81,77,84,80,97,87,70,65,90)
temperature_celcius = (temperature - 32) / 1.8000
sales
temperature 

# plotting scatter graph for sales ~ temperature
library(ggplot2)
ggplot(data.frame(sales,temperature), aes(x = temperature , y=sales , color = ..y..)) +
  geom_point(size=4) +
  labs(
    title = "Fig.1 Sales ~ Temperature", # adds title
    x = "Temperature (°F)", # x-axis label
    y = "Sales\n", # y-axis label
    color = "Sales" # color legend
  ) + 
  scale_color_gradient(low="pink", high="red") +
  theme_light() +
  theme(
    plot.title = element_text(hjust = 0.5),
  )
## plot(sales,temperature)

# getting mean of temperature
mean_temperature <- mean(temperature)
mean_temperature

# Removing From Index 15
sales <- c(sales[-3])
sales
# Insert 16 at 2 index
sales <- append(sales,16,2)
sales 

# creating Vectors of String/Names
names <- c("Tom","Dick","Harry")
names


matrixx <- matrix(c(1:10),nrow=5,byrow=FALSE) # creating Matrix of 2 column and 5 row
matrixx

# creating dataFrame from sales, temperature
icSales <- data.frame('Sales'= sales,'Temperature' = temperature)
icSales

print(str(icSales))

# finding summary of Data Frame
summaryx = summary(icSales)
summaryx


student_data = read.csv("./Student.csv") # Opening Student.csv file
names(student_data) # Printing Variables of Student.csv
```